Simulations

### 2023-11-01 simulation.qmd
Add metadata

---
title: "Simulation"
execute: 
  cache: true
format: 
  html:
    toc: true
    code-fold: true
---

@@

In this document we specify, simulate, and validate a univariate latent means brms model. Code based on Joran's blog post at <https://experienced-sampler.netlify.app/post/stan-hierarchical-ar/>.

# Data

We first set up the data simulation. I used [this code](https://experienced-sampler.netlify.app/post/stan-hierarchical-ar/#testing) but put it inside a function.

@@

## Stan model

@@

## brms

@@

# Next

>>>>

---
title: "Simulations"
subtitle: "Specification and simulation of brms latent means model"
authors:
  - name: Matti Vuorre
    email: mjvuorre@uvt.nl
    url: https://vuorre.com
    orcid: 0000-0001-5052-066X
    affiliation:
      - ref: 1
  - name: Joran Jongerling
    orcid: 0000-0001-5697-1381
    affiliation:
      - ref: 1
affiliations:
  - id: 1
    name: Tilburg University
execute: 
  cache: true
  error: true
format: 
  html:
    theme: materia
    toc: true
    code-fold: true
---

Here we simulate from, specify, and validate latent means models with brms.

@@

# Univariate model

The data simulation and Stan code here is based on [Joran's blog post](https://experienced-sampler.netlify.app/post/stan-hierarchical-ar/).

## Data

We first set up the data simulation.

@@

### Stan model

@@

### brms

@@

# Multivariate model
